Supplemental Materials, Methods and Results

### 2021-05-09 supp.Rmd
Added in local adaptation contrasts for male display and courtship. THere are some problems iwth male display that need to be sorted. For some reason they are not estimating one paramter for Achromatic. gular.

  # Planned contrast. Fit the model in a slightly different way ********************** UP TO HERE
  DisplayBgrd$pop_back_region <- with(DisplayBgrd, interaction(Population, Background_pop, BodyRegion))
  DisplayBgrd_pop_back_region <- lmer(dL ~ pop_back_region + (1|ID), data = DisplayBgrd) 
  summary(DisplayBgrd_pop_back_region)

  robust_DisplayBgrd_pop_back_region <- clubSandwich::conf_int(DisplayBgrd_pop_back_region, cluster = DisplayBgrd$ID, vcov =  "CR2")

  # Contrasts hypothesis tests, but use RVE 
    result_DisplayBgrd_pop_back <- Wald_test(DisplayBgrd_pop_back, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
    result_DisplayBgrd_pop_back$p_val_bonfer <- sapply(p.adjust(result_DisplayBgrd_pop_back$p_val, "bonferroni"), function(x) p_value(x))

  # Grab contrasts that we need from the robust esatimtes
  p_displ_AC <- result_DisplayBgrd_pop_back[2,8]
   CI_dis_AC <- data.frame(Estimate=robust_DisplayBgrd_pop_back$beta[3],
                           lwr = robust_DisplayBgrd_pop_back$CI_L[3],
                           upr = robust_DisplayBgrd_pop_back$CI_U[3])

@@

   # Fit the interaction model
    DispBgrdCC_inter <- lmer(dS ~ Population  + Background_pop + Population:Background_pop + (1|ID), data=DisplayBgrd)
    summary(DispBgrdCC_inter)

    # Fit the main effect model
          DispBgrdCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
          summary(DispBgrdCC)

    # Looks like weak evidence for interaction    
        anova(DispBgrdCC_inter, DispBgrdCC)

@@

    # Planned contrasts. Refit model in slight different form
      DisplayBgrd$pop_back <- with(DisplayBgrd, interaction(Population, Background_pop))
    DisplayBgrd_pop_backCC <- lmer(dS ~ pop_back + (1|ID), data = DisplayBgrd)

    # Fit Robust model
    robust_DisplayBgrd_pop_backCC <- clubSandwich::conf_int(DisplayBgrd_pop_backCC, cluster = DisplayBgrd$ID, vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_DisplayBgrd_pop_backCC <- Wald_test(DisplayBgrd_pop_backCC, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
      result_DisplayBgrd_pop_backCC$p_val_bonfer <- sapply(p.adjust(result_DisplayBgrd_pop_back$p_val, "bonferroni"), function(x) p_value(x))

    # Grab contrasts that we need from the robust esatimtes
      p_displ_CC <- result_DisplayBgrd_pop_backCC[2,8]
       CI_Disp_CC <- data.frame(Estimate=robust_DisplayBgrd_pop_backCC$beta[3],
                               lwr = robust_DisplayBgrd_pop_backCC$CI_L[3],
                               upr = robust_DisplayBgrd_pop_backCC$CI_U[3])

>>>>

  # Planned contrast. Fit the model in a slightly different way ********** PROBLEMS HERE TO WORK OUT WITH CS
  DisplayBgrd$pop_back_region <- with(DisplayBgrd, interaction(Population, Background_pop, BodyRegion))
  DisplayBgrd_Hawaii <- DisplayBgrd %>% filter(Population == "Hawaii")
  DisplayBgrd_pop_back_region <- lmer(dL ~ pop_back_region + (1|ID), data = DisplayBgrd_Hawaii) 
  summary(DisplayBgrd_pop_back_region)

  robust_DisplayBgrd_pop_back_region <- clubSandwich::conf_int(DisplayBgrd_pop_back_region, 
                                                               cluster = DisplayBgrd_Hawaii$ID, 
                                                               vcov =  "CR2")

  # Contrasts hypothesis tests, but use RVE 
    result_DisplayBgrd_pop_back_region <- Wald_test(DisplayBgrd_pop_back_region, 
                                             constraints = constrain_pairwise(c(1:16)),
                                             vcov="CR2", tidy = TRUE)
    result_DisplayBgrd_pop_back$p_val_bonfer <- sapply(p.adjust(result_DisplayBgrd_pop_back$p_val, "bonferroni"),
                                                       function(x) p_value(x))

@@

    # Fit the main effect model
          DispBgrdCC <- lmer(dS ~ Population  + Background_pop  + BodyRegion + (1|ID), data=DisplayBgrd)
          summary(DispBgrdCC)

@@

        BodyRegion_CC_Disp <- Wald_test(DispBgrdCC, constraints = constrain_zero(4:6), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

    # Planned contrasts. Refit model in slight different form
    DisplayBgrd_pop_back_regionCC <- lmer(dS ~ -1 + pop_back_region + (1|ID), data = DisplayBgrd_Hawaii)

    # Fit Robust model
    robust_DisplayBgrd_pop_back_regionCC <- clubSandwich::conf_int(DisplayBgrd_pop_back_regionCC, 
                                                            cluster = DisplayBgrd_Hawaii$ID, 
                                                            vcov =  "CR2")

    # Contrasts hypothesis tests, but use RVE 
      result_DisplayBgrd_pop_back_regionCC <- Wald_test(DisplayBgrd_pop_back_regionCC, 
                                                 constraints = constrain_pairwise(c(1:8)), 
                                                 vcov="CR2", tidy = TRUE)

      result_DisplayBgrd_pop_back_regionCC$p_val_bonfer <- 
                                  sapply(p.adjust(result_DisplayBgrd_pop_back_regionCC$p_val, "bonferroni"), 
                                                                  function(x) p_value(x))
